Ornaments as indicators of Social change before and after European contact at Kiwulan, Northeastern Taiwan

### 2019-07-06 analysis/paper/paper.Rmd
update for the map of sampling area

# mapping sampling area
ggplot(data = AD_data) +
  geom_sf(fill = NA) +
  geom_sf(data = sample_units, color = 'red', fill = NA) +
  geom_sf_text(aes(label = `坑號`), alpha = 0.7) +
  theme_minimal() +
  theme(axis.text.x = element_blank(),
        axis.text.y = element_blank())
```

>>>>

# mapping sampling area
ggplot(sample_units) +
  geom_sf(data = AD_data, fill = NA) +
  geom_sf(color = 'red') +
  geom_sf_text(aes(label = `坑號`), alpha = 0.7) +
  theme_minimal() +
  theme_void() 
```
